Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-26 src/tex/ms.tex
Add comments

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
    This frequency dependence provides stronger enhancement or suppression from the birefringence to high frequency components of the GW, and visa versa.
Also, the frequency dependence can break the degeneracy between $\kappa$ and $\iota$, as this would make the effect of the birefringence affect the amplitude ratio differently compared to $\iota$.
To illustrate the frequency dependence of amplitude birefringence, the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.

@@

% Parameter estimation
The major objective of this study is to constrain GW amplitude birefringence, which is represented by the opacity parameter $\kappa$.
To constrain $\kappa$, we perform PE with data from the third GW transient catalog \citep{GWTC-2.1, GWTC-3}, GWTC-3, using Bilby, a Bayesian toolkit for GW data analysis which is able to calculate posteriors of GW parameters based on interferometer data and priors for the parameters in question \citep{Bilby}. 
We set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$, and perform PE using the modified waveforms.
In both case, we use the same PE configuration as in \citet{GWTC-2.1, GWTC-3} for each individual events.
We also perform test to check if the PE could recover the PE done by LIGO-Virgo-KAGRA Collaboration (LVK) in \citet{GWTC-2.1, GWTC-3}.
We set the prior on $\kappa$ to be a $\delta$ function at $0$, which is the same as using GR.
These control tests result can be found in the data release.

\section{Results}
\label{sec:Results}
\subsection{Result on GWTC-3}
% Stacked kappa posterior plot
% \begin{figure}[h]
%     \script{kappa_stacked.py}
%     \includegraphics[width=\columnwidth]{figures/kappa_stacked.pdf}
%     \caption{
%         The posterior of $\kappa$ for all 69 events included in this study.
%         Each color represent a different event.
%         These posterior are used to calculate the population constraint on $\kappa$ in the following.
%     }
%     \label{fig:kappa_stacked}
% \end{figure}

% How to calculate the combined posterior
In figure \ref{fig:kappa_stacked}, we show the individual posterior of $\kappa$ of each events obtained from PE.
We assume $\kappa$ is different for each event, and the population distribution of $\kappa$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
We then performed hierarchical modeling to construct the likelihood function of $\mu$ and $\sigma$ given interferometer data.
To sample the posterior distribution of $\mu$ and $\sigma$, we used a generic sampling package, flowMC \citep{flowMC}, with prior of $\mu$ and $\sigma$ being uniform distributions.
The posterior of $\mu$ and $\sigma$ are shown in figure \ref{fig:corner_Gaussian}.
The mean of $\mu$ and $\sigma$ are \variable{output/Gaussian_mean.txt}, respectively.

@@

% Case: GW150914 (example of broken degeneracy)
\subsection{Result on GW150914}
Some events have bimodal $\kappa$ distribution, but before we show a bimodal event, we should understand the mechanism of a unimodal $\kappa$ distribution.
Consider GW150914, the first GW detected by LIGO.
In figure \ref{fig:corner_GW150914}, we show the posteriors of the parameters of GW150914.
With the frequency independent birefringence model, the posteriors for $\cos\iota$ look different from the posteriors assuming GR.
This is because, for a nonprecessing system, there is a degeneracy between $\kappa$ and $\iota$ if the frequency dependence is not included.
To reconstruct the amplitude ratio from the interferometer data, an $\iota$ representing a more face-off inspiral can pair with a positive $\kappa$, or an $\iota$ representing a more face-on inspiral with a negative $\kappa$.
As a result, many pairs of $\iota$ and $\kappa$ can be plausible with the frequency independence.

@@

>>>>

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
This frequency dependence provides stronger enhancement or suppression from the birefringence to high frequency components of the GW, and visa versa. \kw{Redundant.}
Also, \kw{You don't need an also here since you are still talking about the same thing} the frequency dependence can break the degeneracy between $\kappa$ and $\iota$, as this would make the effect of the birefringence affect the amplitude ratio differently compared to $\iota$.
To illustrate the frequency dependence of amplitude birefringence, the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.

@@

% Parameter estimation
The major objective of this study is to constrain GW amplitude birefringence,
which is represented by the opacity parameter $\kappa$. To constrain $\kappa$,
we perform PE with data from the third GW transient catalog \citep{GWTC-2.1,
GWTC-3}, GWTC-3, using Bilby, a Bayesian toolkit for GW data analysis which is
able to calculate posteriors of GW parameters based on interferometer data and
priors for the parameters in question \citep{Bilby}. We set the prior on
$\kappa$ to a uniform distribution between $-1$ and $1$, and perform PE using
the modified waveforms. In both case, we use the same PE configuration as in
\citet{GWTC-2.1, GWTC-3} for each individual events. We also perform test to
check if the PE could recover the PE done by LIGO-Virgo-KAGRA Collaboration
\kw{State that this is a sanity check} (LVK) in \citet{GWTC-2.1, GWTC-3}. We set
the prior on $\kappa$ to be a $\delta$ function at $0$, which is the same as
using GR \kw{This sentence kind of read odd. Add conjunction to link it to the
GR test.}. These control tests result can be found in the data release.
\kw{Link}

\section{Results}
\label{sec:Results}

\kw{Looking at the current draft, I do think maybe we should first talk about
 individual constraints first, then population constraints. Tho we should give a
 brief summary of the structure at the beginning of this section}
\subsection{Result on GWTC-3}
% Stacked kappa posterior plot
% \begin{figure}[h]
%     \script{kappa_stacked.py}
%     \includegraphics[width=\columnwidth]{figures/kappa_stacked.pdf}
%     \caption{
%         The posterior of $\kappa$ for all 69 events included in this study.
%         Each color represent a different event.
%         These posterior are used to calculate the population constraint on $\kappa$ in the following.
%     }
%     \label{fig:kappa_stacked}
% \end{figure}

% How to calculate the combined posterior
In figure \ref{fig:kappa_stacked}, we show the individual posterior of $\kappa$
of each events obtained from PE. \kw{Rewrite the following paragraph in the
following way: 1. There are a set of measured $\kappa$ 2. State that there can
either be a single true $\kappa$ or a distribution of $\kappa$ 3. Describe
hierarchical Bayesian, which is essentially stacking the individual results
together. 4. Your choice of model and reason behind such choice.} We assume
$\kappa$ is different for each event, and the population distribution of
$\kappa$ is a Gaussian distribution with mean $\mu$ and standard deviation
$\sigma$. We then performed hierarchical modeling \kw{Need to describe what
hierarchical modelling is} to construct the likelihood function of $\mu$ and
$\sigma$ given interferometer data. To sample the posterior distribution of
$\mu$ and $\sigma$, we used a generic sampling package, flowMC \citep{flowMC},
with prior of $\mu$ and $\sigma$ being uniform distributions. The posterior of
$\mu$ and $\sigma$ are shown in figure \ref{fig:corner_Gaussian}. The mean of
$\mu$ and $\sigma$ are \variable{output/Gaussian_mean.txt}, respectively.

@@

% Case: GW150914 (example of broken degeneracy)
\subsection{Result on GW150914}
Some events have bimodal $\kappa$ distribution, but before we show a bimodal
event, we should understand the mechanism of a unimodal $\kappa$ distribution.
\kw{Just say what you are trying to say, instead of leaving a cliff hanger}
Consider GW150914, the first GW detected by LIGO. In figure
\ref{fig:corner_GW150914}, we show the posteriors of the parameters of GW150914.
With the frequency independent birefringence model, the posteriors for
$\cos\iota$ look different from the posteriors assuming GR. This is because, for
a nonprecessing system, there is a degeneracy between $\kappa$ and $\iota$ if
the frequency dependence is not included. To reconstruct the amplitude ratio
from the interferometer data, an $\iota$ representing a more face-off inspiral
can pair with a positive $\kappa$, or an $\iota$ representing a more face-on
inspiral with a negative $\kappa$. As a result, many pairs of $\iota$ and
$\kappa$ can be plausible with the frequency independence. \kw{Many pairs
doesn't mean bimodelity, you should say why the middle part is constrained to be small as well.}

@@

\kw{Mention two things that drive the population constrain to be better: better event (which you already did), and more events}
